Regular singular Volterra equations on complex domains

### 2023-08-10 reg-sing-volterra.tex
Revise thm:basic_volterra and thm:proto-growth
Add introductory text. Revise the statements, moving both of the the regularity
results into thm:proto-growth. Start reorganizing the proof sections to match.

\item \textit{(Veronica)} Revise introduction, if desired.

@@

\subsection{Main results}\label{sec:results}
%%\begin{defn}\label{fin-order}
%%Consider a Volterra operator $\mathcal{V}$ of the form
%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
%%\begin{itemize}
%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
%%\end{itemize}
%%and at one of the following holds:
%%\begin{enumerate}
%%\item\label{case:0th-order} $m$ isn't the zero function.
%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
%%\end{enumerate}
%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
%%\end{defn}
\begin{thm}\label{thm:basic_volterra}
Let $\hardpart$ be the operator described in Section~\ref{setting:basic} and assume it satisfies {\em Condition \eqref{cond:sing}}. Then the regular singular Volterra equation
\[ f = \hardpart f \]
have the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
f_0(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.

@@

%%The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to zero. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
\end{thm}
We'll prove this result in Section~\ref{sec:proto-construction-regularity}: by Proposition~\ref{prop:construction} we show that $f_0$ is a solution, and by Proposition~\ref{prop:asymptotic at zero} we show that it scales as desired as $\zeta$ goes to zero.

\begin{rmk}
If $q$ has a limit at $\zeta = 0$, the solution $f_0$ from Theorem~\ref{thm:basic_volterra} can be written as a constant mutiple of $\zeta^{\tau-1}$ plus a function which is $O(\zeta^\tau)$ at $\zeta = 0$.

\textcolor{RoyalBlue}{$f_0 \in F\zeta^{\tau-1} + O(\zeta^\tau)$ near $\zeta = 0$ for some non-zero constant $F$.}
\end{rmk}
\begin{thm}\label{thm:proto-growth}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}} and {\em \eqref{cond:slow}} from Section~\ref{setting:basic}. Then the solution $f_0$ from {\em Theorem~\ref{thm:basic_volterra}} is uniformly of exponential type $\lambda_0$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $. We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}

We'll prove this result in Section~\ref{sec:proto-construction-regularity}, Proposition~\ref{prop:asymptotic at infinity}.
\begin{thm}\label{thm:general_volterra}
In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}. Then the Volterra equation
\[f = \volterra f\]
has a unique solution $f$ in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.

@@

\begin{align*}
    |k(a,a')&\leq |\hardker(a,a')| + |\softker(a,a')|\\
    &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert +\frac{\tau}{|\zeta(a)|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
    &\leq \varepsilon +\frac{\tau}{|\zeta(a)|} + \textcolor{magenta}{C_k}\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta (2\delta)}\\
    &\leq \frac{\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} }{|\zeta(a)|}
\end{align*}

@@

\subsubsection{Construction}\label{sec:construction}

\begin{prop}\label{prop:construction}
    The function 
    \begin{equation}%%\label{eqn:test_solution}
    f_0(a)=\frac{p(b)}{p(a)} \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]
   \end{equation}
is a solution of the Volterra equation $\hardpart f_0=f_0$, for some $b\in\Omega$. We call $f_0$ a prototype solution.  
\end{prop}

\begin{proof}
    Let $\psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \psi_0 = -\frac{q}{p} \psi_0\;d\zeta $. Hence, for every $a\in\Omega$ 
    \begin{align*}
        \big[\hardpart f_0\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
        &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\psi_0 d\zeta \\
        &= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0 d\zeta\\
        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\psi_0  \\
    \end{align*}

@@

The last step uses Condition~\eqref{cond:sing}. 
\end{proof}

\begin{rmk}
   {\em Proposition \ref{prop:construction}} and {\em Proposition \ref{prop:asymptotic at zero}} together prove {\em Theorem \ref{thm:basic_volterra}}. 
\end{rmk}

%In fact, if we assume $q$ to be more regular near $\zeta=0$, we get that $|f_0|/\zeta^{\tau-1}$

\begin{prop}\label{prop:asymptotic at infinity}
    Let $b\in\domain$. Assume $\hardpart$ satisfies {\em Condition} \eqref{cond:slow}. Then the prototype solution $f_0$ constructed in {\em Proposition \ref{prop:construction}} belongs to the function space $\singexp{\tau-1}{\lambda_0}(\domain)$.
\end{prop}

\begin{rmk}
    {\em Proposition \ref{prop:asymptotic at infinity}} is an equivalent formulation of {\em Theorem \ref{thm:proto-growth}}.
\end{rmk}

\begin{proof}[Proof of Proposition~\ref{prop:asymptotic at infinity}]
We choose $\varepsilon>0$, then by Condition \eqref{cond:sing} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$ (arguing as in the proof of Proposition \ref{prop:asymptotic at zero}) we get a uniform bound

@@

Let $\Omega_{a}$ be a simply connected open set $\Omega_a\subset\C$ that touches but doesn't contain $\zeta=a$ and let $\Gamma_a^\theta$ be the ray that leaves $a$ at angle $\theta$. If $\Gamma_a^\theta$ is contained in $\Omega_a$, the Laplace transform $\laplace_{\zeta, a}^{\theta} $ maps functions in $\singexp{\sigma}{\Lambda}(\Omega_a)$ with $\sigma>-1$ and $\textcolor{magenta}{\Lambda}>0$ \textcolor{magenta}{[I don't think we need $\Lambda > 0$. For $\Lambda \le 0$, the Laplace transform should still produce functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$, which in this case will include $z = 0$]} to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > 0$~\cite[Section 5.6]{diverg-resurg-i} \textcolor{magenta}{[I think we want $\Re(z e^{-i\theta}) > \Lambda$]}. It is defined by the formula

\begin{equation}\label{laplace:int} 
    \laplace_{\zeta, a}^{\theta} f := \int_{\Gamma_{a}^\theta} e^{-z\zeta} f\, d\zeta
\end{equation}

@@

\subsubsection{Action on integral operators}\label{L-int-op}
%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, a}$ is defined by \textcolor{orange}{[are we changing the definition of $\partial^{\nu-1}_{\zeta, a}$ so that $a$ is a point, rather than a $\zeta$ value?]}
\[ [\partial^{\nu-1}_{\zeta, a} f](p) := \frac{1}{\Gamma(1-\nu)} \int_{a}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
where $p$ is any point on the position domain $\Omega$ \textcolor{orange}{[let's use a different letter here, since $p$ is already used; maybe $b$ for the base point and $a$ for the evaluation point, to match our discussion of $f_0$]}.

It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{\lambda}{\zeta}{a}\,\fracderiv{\mu}{\zeta}{a} & = \fracderiv{\lambda+\mu}{\zeta}{a} & \lambda, \mu \in (-\infty, 0),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer (see equation~35 in \cite{mladenov2014advanced}).

@@

Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta,a} \varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$ \textcolor{orange}{[under what condition on $\varphi$? can we do this with Proposition~\ref{prop:smoothing}?]} and
\[ \laplace_{\zeta,a}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
for all $\lambda \in (0, \infty)$. This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}%%\label{id:L-mult}
\laplace_{\zeta,a}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,a}^\theta \varphi.
\end{equation}
for all integers $n \ge 0$ and suitable direction $\theta$.

@@

>>>>

\item \textcolor{gray}{\textit{(Veronica)} Revise introduction, if desired.}

@@

\subsection{Main results}\label{sec:results}
We want to show that when $\volterra$ is a regular singular Volterra operator of the kind described in Section~\ref{setting:perturbed}, the equation $f = \volterra f$ has a unique solution of a certain form. For the prototypical operator $\hardpart$ described in Section~\ref{setting:basic}, this solution can be written explicitly.
\begin{thm}\label{thm:basic_volterra}
Suppose $\hardpart$ satisfies {\em Condition \eqref{cond:sing}}. Then the equation
\[ f = \hardpart f \]
has the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
\solproto(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.
\end{thm}
We'll prove this result in Section~\ref{sec:construction}.
\color{Tomato}
\begin{thm}%%\label{thm:basic_volterra}
Let $\hardpart$ be the operator described in Section~\ref{setting:basic} and assume it satisfies {\em Condition \eqref{cond:sing}}. Then the regular singular Volterra equation
\[ f = \hardpart f \]
have the {\em prototype solution}
\begin{equation}%%\label{eqn:test_solution}
f_0(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.

@@

%%The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to zero. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
\end{thm}
We'll prove this result in Section~\ref{sec:proto-construction-regularity}. Proposition~\ref{prop:construction} shows that $f_0$ is a solution, and Proposition~\ref{prop:asymptotic at zero} bounds it as desired near $\zeta = 0$.
\color{RoyalBlue}
\begin{rmk}
If $q$ has a limit at $\zeta = 0$, the solution $f_0$ from Theorem~\ref{thm:basic_volterra} can be written as a constant mutiple of $\zeta^{\tau-1}$ plus a function which is $O(\zeta^\tau)$ at $\zeta = 0$.

\textcolor{SeaGreen}{$f_0 \in F\zeta^{\tau-1} + O(\zeta^\tau)$ near $\zeta = 0$ for some non-zero constant $F$.}
\end{rmk}
\color{black}
%%To control the growth of $\solproto$ away from $\zeta = 0$, we'll assume that $\hardpart$ also satisfies {\em Condition~\eqref{cond:slow}}. Under this condition, $\solproto$ is uniformly of exponential type $\lambda_0$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $. We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.}
The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$. With stronger constraints on $\hardpart$, we can also ensure that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$. The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
\begin{thm}\label{thm:proto-growth}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.

Suppose $\hardpart$ also satisfies {\em Condition~\eqref{cond:slow}}. Then $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}
We'll prove this result in Section~\ref{sec:asymptotics}.
\color{Tomato}
\begin{thm}%%\label{thm:proto-growth}
Suppose $\hardpart$ satisfies both {\em Condition~\eqref{cond:sing}} and {\em Condition~\eqref{cond:slow}} from Section~\ref{setting:basic}. Then the solution $f_0$ from {\em Theorem~\ref{thm:basic_volterra}} is uniformly of exponential type $\lambda_0$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $. We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} In light of the behavior near $\zeta = 0$ described in, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}
We'll prove this result in Section~\ref{sec:proto-construction-regularity}, where it's restated as Proposition~\ref{prop:asymptotic at infinity}.
\color{black}
\begin{thm}\label{thm:general_volterra}
In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}. Then the Volterra equation
\[f = \volterra f\]
has a unique solution $f$ in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.

@@

\begin{align*}
    |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
    &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert +\frac{\tau}{|\zeta(a)|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
    &\leq \varepsilon +\frac{\tau}{|\zeta(a)|} + \textcolor{magenta}{C_k}\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta (2\delta)}\\
    &\leq \frac{\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} }{|\zeta(a)|}
\end{align*}

@@

\subsubsection{Construction}\label{sec:construction}
\color{Tomato}
\begin{prop}\label{prop:construction}
    The function 
    \begin{equation}%%\label{eqn:test_solution}
    f_0(a)=\frac{p(b)}{p(a)} \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]
   \end{equation}
is a solution of the Volterra equation $\hardpart f_0=f_0$, for some $b\in\Omega$. We call $f_0$ a prototype solution.  
\end{prop}
\color{black}
\begin{proof}[Proof of Theorem~\ref{thm:basic_volterra}]
    Let $\psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \psi_0 = -\frac{q}{p} \psi_0\;d\zeta $. Hence, for every $a\in\Omega$ 
    \begin{align*}
        \big[\hardpart f_0\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
        &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\psi_0 d\zeta \\
        &= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0 d\zeta\\
        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\psi_0  \\
    \end{align*}

@@

The last step uses Condition~\eqref{cond:sing}. 
\end{proof}
\color{Tomato}
\begin{rmk}
   {\em Proposition \ref{prop:construction}} and {\em Proposition \ref{prop:asymptotic at zero}} together prove {\em Theorem \ref{thm:basic_volterra}}. 
\end{rmk}
\color{black}
%In fact, if we assume $q$ to be more regular near $\zeta=0$, we get that $|f_0|/\zeta^{\tau-1}$

\begin{prop}\label{prop:asymptotic at infinity}
    Let $b\in\domain$. Assume $\hardpart$ satisfies {\em Condition} \eqref{cond:slow}. Then the prototype solution $f_0$ constructed in {\em Proposition \ref{prop:construction}} belongs to the function space $\singexp{\tau-1}{\lambda_0}(\domain)$.
\end{prop}
\color{Tomato}
\begin{rmk}
    {\em Proposition \ref{prop:asymptotic at infinity}} is an equivalent formulation of {\em Theorem \ref{thm:proto-growth}}.
\end{rmk}
\color{black}

%%\begin{proof}[Proof of Proposition~\ref{prop:asymptotic at infinity}]
\begin{proof}
We choose $\varepsilon>0$, then by Condition \eqref{cond:sing} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$ (arguing as in the proof of Proposition \ref{prop:asymptotic at zero}) we get a uniform bound

@@

Let $\domain_\alpha$ be a simply connected open set $\domain_\alpha\subset\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$. If $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, the Laplace transform $\laplace_{\zeta, a}^{\theta} $ maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > \Lambda$~\cite[Section 5.6]{diverg-resurg-i}. It is defined by the formula

\begin{equation}\label{laplace:int} 
\laplace_{\zeta, \alpha}^{\theta} f := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} f\, d\zeta
\end{equation}

@@

\subsubsection{Action on integral operators}\label{L-int-op}
%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
\[ [\partial^{\nu-1}_{\zeta, \alpha} f](a) := \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu} f\,d\zeta \]
for each $a \in \domain_\alpha$.

It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{\nu}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\nu+\mu}{\zeta}{\alpha} & \nu, \mu \in (-\infty, 0),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer (see equation~35 in \cite{mladenov2014advanced}).

@@

Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that if $\partial^{-\nu}_{\zeta,a} \varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$ \textcolor{orange}{[under what condition on $\varphi$? can we do this with Proposition~\ref{prop:smoothing}?]} and
\[ \laplace_{\zeta,a}\,\partial^{-\nu}_{\zeta} \varphi = z^{-\nu} \laplace_{\zeta, a} \varphi \]
for all $\nu \in (0, \infty)$. This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}%%\label{id:L-mult}
\laplace_{\zeta,a}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,a}^\theta \varphi.
\end{equation}
for all integers $n \ge 0$ and suitable direction $\theta$.

\begin{rmk}
    Increasing the regularity in the position domain, then the Laplace transform gives something which is faster decaying in the frequency domain. This is a general feature of the Laplace transform.
\end{rmk}

@@

Finally, we look closer to the prototype solution $f_{0,\alpha}$ from Theorem \ref{thm:basic_volterra}, Equation \eqref{eqn:test_solution}. Following the computation we did above we get that

\begin{align*}
    f_{0,\alpha}(a)&=\frac{p(b)}{p(a)} \exp\left(-\int_b^a\frac{q}{p} d\zeta\right)\\
    &=\frac{p(b)}{p(a)} \frac{(\zeta(a)-\alpha)^{\tau_\alpha}}{(\zeta(b)-\alpha)^{\tau_\alpha}} \exp\left(-\int_b^a\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} d\zeta\right)\\
    &=(\zeta(a)-\alpha)^{\tau_\alpha-1} \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}} \frac{1}{p'(\alpha)+b_2'(\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2}
\end{align*}
